Exploratory Analysis

### 2025-12-04 Exploratory Analysis.Rmd
Attempting clustering (merged data, no lags)

# This merge is only keeping the rows that are in both data frames
# Not using df3 because I don't want our target variables to be included in the clustering
merged = df1 %>% inner_join(df2, by = "Date")
merged$Date = NULL # We already have the Timestamp column

@@

ggplot(merged, aes(x = cluster_data[ , "mean_Temp"], y = cluster_data[ , "mean_pH"], # you can compare any two columns
                   color = factor(cluster))) +
  geom_point() +
  labs(title = "K-Means Clustering", color = "Cluster") +
  theme_bw()

>>>>

# This merge is only keeping the rows that are in both data frames
# Not using df3 because I don't want our target variables to be included in the clustering
merged = df1 %>% 
  inner_join(df2, by = "Date")
merged$Timestamp = NULL # We'll keep the Date column

@@

cluster_plot = merged %>% 
  inner_join(df3, by = "Date")

# You can change the names to see different variables and their clusters
ggplot(merged, aes(x = cluster_plot[ , "mean_Turbidity"], y = cluster_plot[ , "Ferric.chloride..mg.L"], # you can compare any two columns
                   color = factor(cluster))) +
  geom_point() +
  labs(title = "K-Means Clustering", color = "Cluster") +
  theme_bw()
